\section{Hostile-referee attack map}
\label{app:attack-map}
\begin{fixedbox}
\textbf{Use after Tier~3 hardening.} For the present Zenodo manuscript, the core theorem spine is carried locally in Sections~2--8. This appendix therefore routes objections first to the in-manuscript theorem ladder. Corpus documents remain relevant only for downstream consequence layers, source provenance, or audit posture outside the local spine.
\end{fixedbox}

\begin{longtable}{P{0.34\textwidth}P{0.28\textwidth}P{0.26\textwidth}}
\caption{Hostile-reader attack map for the hardened manuscript}\\
\toprule
\textbf{To keep this objection alive, deny at least one of:} & \textbf{Primary denial target} & \textbf{Why this is the right place to attack} \\
\midrule
\endfirsthead
\toprule
\textbf{To keep this objection alive, deny at least one of:} & \textbf{Primary denial target} & \textbf{Why this is the right place to attack} \\
\midrule
\endhead
\bottomrule
\endfoot
The target class is a protective narrowing rather than the minimal domain in which proposition-bearing reasoning remains assessable. & \S\,2 & The manuscript now carries the assessability-boundary argument locally, so this attack must engage the local theorem spine rather than a corpus-level dependency claim. \\
The kernel is merely a presentational starting point or a weak axiom block rather than a derived floor. & \S\,2 & Section~2 now bears the local forcing burden for kernel emergence, non-derivability, minimality, and no-lower-generator closure. \\
State-transition form is only a modeling preference. & \S\,3 & The modeling theorem, identity persistence, irreversible commitment, and coherence meta-theorem are now local; the attack must therefore deny the section's explicit forcing chain. \\
The AMetric boundary is assumed rather than derived. & \S\,4 & Section~4 now carries the local symmetry, equality-pattern, no-selector, no-order, no-metric, and no-deeper-invariant ladder. \\
Uniqueness of the admissible interior is merely announced. & \S\,5 & The standing-regime section now proves gate uniqueness, standing emergence, no repairs / no generators / no carriers, quotient closure, and unique interior locally. \\
Admissibility and standing remain distinct analytical dimensions or dual-track governance survives on the fixed domain. & \S\,5 & Section~5 now proves the same-scope equivalence and blocks residual dual-track governance locally. \\
The same-domain discriminator space is not actually exhausted; some sixth same-scope route still survives. & \S\,5 & The local quotient and factorization theorems force same-scope standing-relevant discriminators to factor through the standing quotient; non-factorization is itself the illicit-authority witness. \\
Mathematics can still reopen the interior through forcing, completion, compactness, choice, or other operator families. & \S\,6 & The operator-exhaustion layer is now local and explicitly carries no same-scope totalization, conservative extension collapse, family-wise closure, and interaction closure. \\
G\"odel, semantic truth, infinitary rules, or same-domain extension reopen the closure theorem from above. & \S\,8 & Section~8 now contains the explicit incompleteness-attack defeat, including code-role exhaustion, route exhaustion, and same-domain non-instantiability. \\
Physics still generates standing through descriptive or metric richness. & \S\,7 & This remains the softest claim layer of the local manuscript and is the correct place to attack if one rejects the physics-facing descriptive discipline. \\
Mathematics grounds physics, physics grounds mathematics, or a meta-level platform reinstalls privilege. & \S\,9 & Section~9 is now explicitly downstream and classificatory; an objector must therefore deny the synthesis as a post-closure classification result rather than as a hidden second foundation. \\
The downstream application manuscripts are hidden premises of the foundational arc. & \S\,10 together with Theorem~\ref{thm:no-downstream-backflow} & Section~10 fixes the one-way consequence posture and blocks downstream-to-foundation backflow explicitly. \\
The periodic Navier--Stokes roadmap is invalid because the official theorem would have to be proved by a standard constructive PDE continuation argument. & \S\,10 together with Proposition~\ref{prop:method-neutral-roadmaps} and \nsdoc{} as theorem roadmap only & This objection now lands wholly in the downstream roadmap layer, not in the foundational spine. \\
The Yang--Mills roadmap overclaims universality or hides endpoint restrictions. & \S\,10 together with the Yang--Mills roadmap & This is a downstream roadmap objection only and no longer bears on the local theorem spine. \\
The measurement consequence is only semantic redescription and not closure-relevant. & \S\,10 together with \measurementdoc{} & This is also downstream consequence-facing only; the attack cannot now be used to reopen Sections~2--8. \\
The formalization claims are overstated. & \S\,11 and Appendix~\ref{app:formalization-map} & The manuscript now separates local proof force from documented formalization posture more sharply; an objector must engage the exact documented level claimed. \\
The capstone still rests on dispensable closure premises that could be weakened without reopening anything essential. & \S\,11 together with Theorem~\ref{thm:axiom-necessity-layer} and Corollary~\ref{cor:formal-closed-system-seal} & The final audit section exposes premise-necessity and forces the critic either to deny a named premise, deny a theorem depending on it, or declare scope change. \\
\end{longtable}

\begin{riskbox}
\textbf{Use of the map.} For the hardened manuscript, slogan-level objections are no longer enough against the core theorem spine. A critic must now deny a local section theorem, or else move explicitly into the downstream consequence layers where import posture is openly declared.
\end{riskbox}
