\section{Matter--antimatter asymmetry and admissible baryogenesis}
\label{app:baryogenesis}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \baryogenesisdoc{}. It depends on the irreversible-commitment architecture of Section~3, the standing-conservation results of Section~5, and the descriptive closure of Section~7. It introduces no specific baryogenesis mechanism and no modification of Standard Model dynamics.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is persistent matter--antimatter asymmetry under irreversible cosmic evolution, with baryon identity treated as a bookkeeping label that nonetheless bears standing across cosmic history.

\begin{proposition}[Baryogenesis consequence profile]
If cosmic evolution is irreversible in the admissibility sense and persistent material structure is to preserve standing across that history, then exact global matter--antimatter symmetry is inadmissible as a standing-bearing bookkeeping regime. Some mechanism establishing a net persistent matter asymmetry is therefore structurally required, and baryogenesis is the standard model-building name for that admissible resolution.
\end{proposition}

\begin{proof}
This is the structural conclusion of \baryogenesisdoc{}. The source treats baryon identity as an interaction-defined bookkeeping label, shows that exact global matter--antimatter symmetry would fail to preserve standing once irreversible loss of retrievable correlation structure occurs, and then reclassifies baryogenesis as the admissible resolution of persistent identity bookkeeping rather than as a merely optional dynamical episode. The present appendix imports only that consequence-level necessity and none of the source's microphysical non-claims.\cite{MaleyBaryogenesis}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not select a specific baryogenesis mechanism, derive the baryon-to-photon ratio, require particular CP-violating parameters, or modify Standard Model dynamics. The point is structural: asymmetry is required for standing-preserving identity bookkeeping under irreversible evolution.\cite{MaleyBaryogenesis}
\end{reviewbox}
