\section{Black holes without interior facts}
\label{app:black-holes}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \blackholesdoc{}. It depends on the fixed-domain reference and fixation discipline already carried by Sections~5, 7, and 8 and introduces no new quantum-gravity dynamics.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is the black-hole horizon as a fixation boundary for truth-apt physical claims.

\begin{proposition}[Black-hole fixation consequence profile]
On the fixed closure substrate, event horizons are to be read as fixation boundaries rather than as access points to a globally referencible interior fact-domain. Once that reclassification is enforced, the information paradox, firewall necessity, interior microstate ontology, and strong holographic upgrades are dissolved as category errors on the original scope, while exterior general relativity, Hawking radiation, and boundary thermodynamics remain unchanged.
\end{proposition}

\begin{proof}
This is the exact diagnostic payoff of \blackholesdoc{}. The source identifies horizons as fixation boundaries, distinguishes fixation failure from ordinary epistemic ignorance, blocks diachronic identity claims for non-fixable interior referents, and then shows that global bookkeeping demands across the horizon presuppose precisely the interior facthood that the fixation analysis rules out. The present appendix imports only that paradox-dissolution claim. Exterior black-hole physics is preserved because the source explicitly leaves locally anchored exterior observations, boundary thermodynamics, and Hawking-radiation bookkeeping intact.\cite{MaleyBlackHoles}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not modify general relativity, quantum field theory, or any observationally anchored exterior black-hole physics. It dissolves only the inadmissible demand that a non-fixable black-hole interior nevertheless constitute a domain of truth-apt globally referencible facts.\cite{MaleyBlackHoles}
\end{reviewbox}
