\section{Entanglement as boundary-level compatibility}
\label{app:entanglement}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \entanglementdoc{}. It consumes the AMetric boundary, standing conservation, and uniqueness-of-interior results of Sections~4, 5, 7, and 9 and introduces no new dynamics, ontology, or hidden variables.
\end{fixedbox}

\subsection*{Scope and dependency declaration}
The fixed-domain object is a Bell scope consisting of Bell-violating, no-signaling bipartite quantum correlations. The appendix assumes the imported substrate already fixed in the main text: stable reference, lawful redescription, irreversible commitment, AMetric boundary discipline, bivalent admissibility, standing as reuse-stable admissibility, uniqueness of the admissible interior on a fixed scope, and anchor/tensor/skin role discipline.

\subsection*{Claim type}
This appendix is a compact consequence profile. It uses \entanglementdoc{} only for the fixed-scope interpretive payoff that survives once the Bell data are read through the capstone's closure theorems.

\begin{proposition}[Bell-scope consequence profile]
On the fixed Bell scope, an entangled preparation is a joint standing class carrying tensor-level compatibility rather than two independently sufficient local standing states; a local measurement is an admissible skin selection within that already admitted joint class rather than a tensor-changing act; and same-scope hidden-variable, signaling, mechanism, and repair readings are thereby eliminated.
\end{proposition}

\begin{proof}
This is the exact structural result stated in \entanglementdoc{}. The source reclassifies entangled preparations as joint standing classes whose load-bearing content is quotient-level tensor compatibility; treats local measurement as admissible skin selection rather than tensor change; preserves no-signaling by denying any same-scope transfer, repair, or carrier route; and then eliminates Bell-local hidden-variable completion, superluminal signaling, tensor-to-mechanism upgrades, and same-scope repair readings on the original Bell scope. The capstone imports only that downstream classification, not a new proof source for its own AMetric, conservation, or uniqueness theorems.\cite{MaleyEntanglementBoundary}
\end{proof}

\begin{corollary}[Unique same-scope Bell reading]
Once the Bell data and the imported substrate are fixed, the boundary-level compatibility reading of entanglement is not one admissible option among several same-scope readings; it is the unique same-scope admissible reading up to lawful redescription.
\end{corollary}

\begin{proof}
The source manuscript makes the uniqueness point explicit: once the admissible interior is unique on the fixed scope, the surviving Bell reading is not merely preferred but forced. Any purported rival same-scope reading is therefore either skin-level paraphrase of the same tensor content, hidden load, or scope change.\cite{MaleyEntanglementBoundary}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not derive the Hilbert-space formalism, the Born rule, or the Tsirelson bound from below. It constrains only the admissible interpretation of Bell-type operational data once those data are placed inside the fixed closure substrate.\cite{MaleyEntanglementBoundary}
\end{reviewbox}
