\section{Downstream source-role and proof-home note}
\label{app:final-source-freeze}

\begin{fixedbox}
\textbf{Downstream consequence-facing only.} This appendix is archival packaging downstream of Sections~1--9 and Section~\ref{sec:consequence-pathways}. It records source-role discipline only and does not function as a second proof engine for the foundational arc.\par\medskip
\textbf{Final source-role rule.} No document functions as a live proof source for the capstone unless its role is declared below. Consequence manuscripts, theorem roadmaps, companion proof homes, and provenance-only documents do not become live dependencies by proximity, familiarity, or later convenience.\par\medskip
\textbf{Core proof-home rule.} Sections~1--8 now carry the load-bearing theorem spine locally. The source-role freeze below therefore governs only (i) provenance and audit traceability for that local spine and (ii) downstream consequence typing beyond it. A cited source is not thereby a live premise unless this appendix says so.\par\medskip
\textbf{Zenodo posture.} The appendix atlas extends explanatory and consequence coverage only. It does not silently reopen the foundational burden of the main theorem chain.
\end{fixedbox}

\subsection*{Live proof sources for the foundational arc}

\begin{itemize}
  \item \fcas{}: target class, kernel forcing, non-derivability, minimality, mechanization boundary, and the documented fixed-kernel Lean surface.
  \item \ametric{}: canonical state-transition representation, coherence necessity, the coherence meta-theorem, governance-level bivalence, state-transition normal form of bivalence, pre-fixational non-reference, relabeling symmetry, equality-pattern completeness, no selector / no order / no metric beyond equality, boundary non-action, no deeper invariant, singleton meta-necessity, and the derived AMetric-boundary axiom.
  \item \trajpaper{}: finite fixed-scope trajectory closure, prefix and composition geometry, lawful redescription invariance, irrecoverability of coherence failure, local fixed-substrate closure, and the documented theorem-level / theorem-family Lean correspondence.
  \item \necessitydoc{}: the fixed-domain pre-boundary no-faithful-lower-generator hardening used in Section~\ref{sec:ametric-boundary}, together with gate existence, standing emergence, no same-act repair, no generators, no independent carriers, standing conservation, unique admissible interior, and the same-domain extension-stable no-lower-generator hardening used in Section~\ref{sec:kernel-floor}.
  \item \standeqdoc{}: the positive equivalence closure between admissibility and standing used in Section~\ref{sec:standing-regime} to eliminate every residual dual-track governance form.
  \item \atsdoc{}: the standing-quotient universal property, soundness/completeness of standing presentations, standing-quotient uniqueness, role exhaustiveness, and skin non-authority in derived form.
  \item \trajpaper{} (in its fixed-substrate closure role): the no-stricter-refinement theorem showing that no admissibility-preserving standing generator survives beneath tensor content on the fixed substrate.
  \item \unusdoc{}: the typed-domain closure packaging that makes discrete multiplicity elimination and apex uniqueness explicit for the admissible interior.
  \item \exhaustiondoc{}: typed boundary discipline, quotient-factorization against same-scope standing-relevant discriminators, and the necessity-layer witnesses by which any remaining internal objection must identify the governing premise it denies.
  \item \sameoperatorsdoc{}: graph rigidity on the standing-bearing carrier, no same-scope totalization, the five covered mechanisms for apparent same-scope totalization, family-wise operator closure, interaction closure, and the global closure-by-exhaustion theorem for mathematics.
  \item \clausuradoc{}: conservative extension collapse, interpretability collapse, the finite standing-extending-operator schema, mathematics closure, physics closure, fixation split, and the capstone closure engine.
  \item \fixedbasedoc{}: predecessor and cross-check for the old-base no-internal-totalization hinge and the auxiliary-data dichotomy in fixed-base language.
  \item \noninstgodeldoc{}: same-domain meta-closure, inferential-life exhaustion, code-role exhaustion, G\"odel-threat alignment, the translation filter for ordinary G\"odel objections, rescue-route exhaustion, and same-domain G\"odel non-instantiability.
  \item \eademdoc{}: two-spectrum synthesis, closure parity, mirror classification, prohibition package, and descriptive closure of admissible description.
\end{itemize}

\subsection*{Consequence-facing only under the present source-role freeze}

\begin{itemize}
  \item \measurementdoc{} is consequence-facing only. The capstone preserves its claim class and hardening results --- measurement-reference quotient, equivalence collapse, Everettian non-selection, fixation commutation, selector exhaustion, and denial-condition matrix --- without importing it as a second foundational proof spine.
  \item \structuradoc{} is consequence-facing only. The capstone preserves its witness-normal-form and transport-certificate role without promoting its fixed-load ledger to a new foundational source.
  \item \nsdoc{} is a theorem roadmap only. The capstone preserves its official endpoint, claim-class discipline, same-object convention, one-route dependency audit, and theorem-local denial map, but it does not import the Navier--Stokes manuscript as a premise of Sections~1--9.
  \item \ymmaindoc{} is a theorem roadmap only, and \ymcompanionone{}, \ymcompaniontwo{}, and \ymcompanionthree{} remain proof homes behind that roadmap only. The capstone preserves theorem-level object, theorem map, endpoint hygiene, claim boundaries, and non-claims, but does not reactivate the companions as hidden premises of the foundational arc.
  \item \entanglementdoc{} is consequence-facing only. The capstone uses it to type Bell-scope correlations as joint-standing-class tensor compatibility and to eliminate hidden-variable, signaling, mechanism, and repair readings on that fixed scope; it does not use the manuscript as a premise of Sections~1--9.
  \item \gaugeconstraintdoc{} is roadmap-only in the 42 atlas. The rigidity theorem proved there is not imported as a new proof source. Only its downstream classificatory payoff for canonical GR and selector-bearing quantum formalisms is preserved.
  \item \beginningdoc{} and \interiorenddoc{} are consequence-facing only. The capstone preserves their licensing-side and exhaustion-side classifications of the admissible interior without importing either manuscript as a premise of the kernel, standing, or closure theorems.
  \item \baryogenesisdoc{} is consequence-facing only. The capstone preserves its identity-persistence payoff under irreversible cosmic evolution without importing any microphysical mechanism claim into the foundational arc.
  \item \blackholesdoc{} is consequence-facing only. The capstone preserves its fixation-boundary diagnosis of black-hole interiors without promoting it to a new quantum-gravity source.
  \item \lifedoc{} is consequence-facing only. The capstone preserves its structural roles for life, intelligence, and technology without importing biochemical, probabilistic, or anthropic claims into the foundational arc.
  \item \minddoc{} is roadmap-only in the 42 atlas. The capstone preserves its structural rigidity payoff without importing the source's full proof-granularity ladder as a second foundational theorem spine.
  \item \metanecessitydoc{} is consequence-facing only. Its proof-of-proof corollaries on irreversibility, temporal asymmetry, and informational non-primitivity are carried over only as downstream consequences and not as replacements for the capstone's own kernel derivation.
  \item \metamysterydoc{} is consequence-facing only. The capstone preserves its eliminative diagnostic for persistent mystery and dark-sector patch cascades without allowing it to backflow into Sections~1--9.
\end{itemize}

\subsection*{Not claimed as live proof sources}

\begin{itemize}
  \item No unified capstone Lean development or capstone-wide theorem register beyond what the declared sources document.
  \item No dormant or privately circulated manuscript promoted after the present freeze.
  \item No slides, oral explanations, or unpublished notes.
  \item No source-level hardening from a downstream manuscript may be treated as theorem-bearing for the foundational arc unless the source set is explicitly reopened and the theorem order rebuilt.
\end{itemize}

\begin{reviewbox}
\textbf{Interpretive consequence.} The capstone is stable against theorem drift only if these role distinctions are kept literal. A proof home is not automatically a live premise. A theorem roadmap is not automatically part of the foundational arc. A consequence profile is not a hidden reconstruction of the main theorem chain. The Zenodo appendix atlas therefore extends explanatory coverage only by strict consequence typing, never by silent backflow into the locally proved spine.
\end{reviewbox}
