\section{End of the admissible interior}
\label{app:interior-end}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \interiorenddoc{}. It depends on the standing and physics-closure package of Sections~5 and 7 and introduces no new modal, thermodynamic, or cosmological primitives.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is terminal exhaustion of admissible redescription under fixed admissibility constraints.

\begin{proposition}[End-side consequence profile]
Admissibility constraints are necessary but not sufficient for the persistence of an admissible interior. An admissible interior exists if and only if at least one standing-preserving redescription remains available; exhaustion is the absence of any admissible successor configuration under fixed constraints; and such exhaustion is neither temporal process, thermodynamic depletion, nor evolving-constraint dynamics.
\end{proposition}

\begin{proof}
This is the exact classification established in \interiorenddoc{}. The source defines the admissible interior in terms of the availability of standing-preserving admissible successors, formalizes exhaustion as the empty admissible successor set under fixed constraints, distinguishes realizability failure from failure of admissibility itself, and then reclassifies heat death and related cosmological narratives as terminal metric regimes rather than admissible exhaustion. The present appendix imports only that terminal consequence profile.\cite{MaleyEndInterior}
\end{proof}

\begin{corollary}[No same-scope successor interior]
Once admissible exhaustion obtains on the original scope, no same-scope successor interior and no post-interior physics narrative remains licensed.
\end{corollary}

\begin{proof}
The source manuscript states this as a direct consequence of exhaustion: fixed admissibility constraints remain intact, but no standing-preserving continuation survives. Any purported successor interior would therefore require new load, new scope, or illicit modal necessity.\cite{MaleyEndInterior}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not describe a dynamical end-of-time process, vacuum decay, or thermodynamic consumption of admissibility. It classifies only the structurally unremarkable absence of any further admissible configuration under fixed constraints.\cite{MaleyEndInterior}
\end{reviewbox}
