\section{Beginning of the admissible interior}
\label{app:interior-beginning}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \beginningdoc{}. It depends on the AMetric boundary and standing-conservation package already fixed in Sections~4, 5, and 7 and does not introduce an origin narrative, pre-metric dynamics, or causal emergence.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is the first licensed metric regime inside admissibility: the minimal standing condition under which metric surrogates become valid within an already admitted interior.

\begin{proposition}[Beginning-side consequence profile]
If metric description is licensed at all inside an admissible interior, then its first licensed regime is governed by an L-metric boundary, admits no proto-metric partial onset, admits no local metric islands, requires a globally closing metric circuit, and sits at maximal tensor stress so that the surviving admissible redescriptions appear non-classical when written in interior metric language.
\end{proposition}

\begin{proof}
This is the exact structural payload of \beginningdoc{}. The source defines the L-metric boundary as the minimal admissible standing condition for metricity, proves that metric surrogates are co-licensed rather than sequentially switched on, excludes local patchwork onset, proves an initial closure requirement for metricity, and then identifies maximal tensor stress at that first licensed metric regime. The paper's final payoff is that, under maximal tensor stress, the admissible successor structure appears as discretization, global consistency, and barrier-penetration behavior when translated into interior metric language. The present appendix imports only that beginning-side classification.\cite{MaleyBeginningInterior}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not describe how admissibility arises, how the AMetric boundary is established, or why an admissible interior exists. ``Beginning'' is used strictly as a licensing notion and not as a temporal origin, causal process, or pre-metric dynamical regime.\cite{MaleyBeginningInterior}
\end{reviewbox}
