\section{Standing localization, life, intelligence, and technology}
\label{app:life}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \lifedoc{}. It depends on the standing-conservation and physics-closure results of Sections~5 and 7 and introduces no biochemical, probabilistic, anthropic, or sociological primitives.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is a non-degenerate admissible physical regime that permits persistent bounded subsystems with nonzero repair capacity.

\begin{proposition}[Standing-localization consequence profile]
In any such regime, standing cannot remain uninstantiated and must localize within bounded repairable subsystems; life is the minimal physical instantiation of that localization; intelligence is a constrained optimization of standing efficiency rather than an inevitable outcome; and sustained technological standing is structurally fragile because nonlocal amplification outruns repair capacity.
\end{proposition}

\begin{proof}
This is the exact consequence package stated in \lifedoc{}. The source proves a standing-localization theorem for non-degenerate admissible physical regimes, identifies life as the minimal localized standing-preserving structure, treats intelligence as contingent optimization rather than necessity, and derives structural instability for long-duration technological standing from the mismatch between nonlocal coupling and local repair. The present appendix imports only that conditional consequence profile and none of the source's explicitly disclaimed biochemical, probabilistic, or anthropic claims.\cite{MaleyStandingLocalizationLife}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not predict molecular substrates, estimate frequencies, appeal to anthropic selection, or offer a sociological narrative of civilizations. It states only the structural roles of life, intelligence, and technology once admissibility and standing conservation are already in force.\cite{MaleyStandingLocalizationLife}
\end{reviewbox}
