\section{Measurement records, referential fixation, and theory-level confirmation}
\label{app:measurement-reference}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a compact consequence profile for \measurementdoc{}. It is conditional on the fixed substrate of Sections~5, 7, and 8 and does not function as a proof source for Sections~1--9.
\end{fixedbox}

\subsection*{Scope and dependency declaration}
The fixed-domain object is the class of admissible reference assignments for measurement records in a physically non-selective theory used to underwrite truth-apt diachronic discourse about memory, anticipation, deliberation, and theory-level confirmation. The appendix consumes the standing regime of Section~5, the physics-closure and descriptive-role discipline of Section~7, and the same-domain route-exhaustion results of Section~8.

\subsection*{Claim type}
This appendix is a compact consequence profile with theorem-facing summary. It preserves the quotient theorem, equivalence collapse, Everettian non-selection, fixation commutation, and selector-exhaustion payoffs of \measurementdoc{} without reproducing its entire theorem ladder.

\begin{proposition}[Measurement-reference consequence profile]
On the fixed downstream substrate, admissible reference assignments for measurement records factor through a unique standing-bearing quotient; bare Everettian branching, entanglement, and decoherence do not by themselves collapse the admissible class to one quotient class; and, absent such collapse, theory-level confirmation, memory, anticipation, and deliberation are assignment-relative rather than theory-relative.
\end{proposition}

\begin{proof}
This is the exact fixed-domain payoff of \measurementdoc{}. The source manuscript proves a measurement-reference quotient theorem, a global equivalence-collapse theorem for same-scope content spaces, an Everettian non-selection theorem, a fixation-commutation hinge for theory-level confirmation, a diachronic inheritance theorem for memory, anticipation, deliberation, and agency, and a selector-exhaustion theorem for interpretation packages. The present appendix imports only that downstream consequence package. By Theorem~\ref{thm:no-downstream-backflow}, none of these results functions as a premise of Sections~1--9.\cite{MaleyMeasurement}
\end{proof}

\begin{corollary}[Measurement-record stabilization trichotomy]
Any discourse-committing completion of a physically non-selective measurement theory must do exactly one of three things on the target discourse: fix singular reference dynamically, fix it by added ontological privileging, or restrict admissible assignments strongly enough that they collapse into one standing-equivalence class. Refusing the target truth-apt discourse is the only remaining non-committing option.
\end{corollary}

\begin{proof}
This is the selector-exhaustion and interpretation-taxonomy consequence carried by \measurementdoc{} once the fixed substrate of the capstone is in place. Dynamic selection, ontic privileging, semantic restriction, and discourse deflation exhaust the same-scope options for fixing singular reference to measurement records.\cite{MaleyMeasurement}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not derive the Born rule, alter the Hilbert-space formalism, or claim that all interpretations of quantum mechanics are equivalent. Its narrower claim is that, on the target explanatory practice, the measurement problem first appears as a problem of referential determinacy for measurement records and only derivatively as a problem of outcome production.\cite{MaleyMeasurement}
\end{reviewbox}
