\section{Meta-necessity, temporal asymmetry, and information non-primitivity}
\label{app:meta-necessity}

\begin{fixedbox}
\textbf{Consequence-facing only.} This appendix is a cross-domain consequence profile for \metanecessitydoc{}. It depends on the kernel, irreversibility, and same-domain closure results of Sections~2--8 and does not replace the capstone's own proof of the kernel floor.
\end{fixedbox}

\subsection*{Fixed-domain object}
The fixed-domain object is any non-degenerate irreversible decision system with unrestricted composition.

\begin{proposition}[Meta-necessity consequence profile]
Any such system must enforce an admissibility invariant sufficient to preserve standing under composition or else fail to define irreversibility itself. On that basis, temporal asymmetry is reclassified as an interior bookkeeping artifact of irreversible fixation, and informational quantities are reclassified as post-admissible bookkeeping rather than ontic primitives.
\end{proposition}

\begin{proof}
This is the exact eliminative and meta-level payoff of \metanecessitydoc{}. The source proves that irreversibility without a standing-preserving invariant is undefined under unrestricted composition, then derives meta-necessity of admissibility, treats operational gate sequences as enforcement surfaces rather than architectural preferences, and adds the arrow-of-time and information corollaries: temporal asymmetry is an artifact of irreversible fixation inside the admissible interior, and informational quantities presuppose fixation, reference stability, and encoding rather than grounding them. The present appendix imports only that corollary package and does not replace the capstone's own derivation of the kernel floor.\cite{MaleyMetaNecessity}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not assert the corpus as semantically true, does not introduce a new primitive information ontology, and does not ground an ontic arrow of time. It classifies only what follows if irreversibility is to remain well-defined under unrestricted composition.\cite{MaleyMetaNecessity}
\end{reviewbox}
