\section{Mind as a structurally rigid interface of admissible evaluation}
\label{app:mind}

\begin{fixedbox}
\textbf{Roadmap-only appendix.} This appendix uses \minddoc{} as a strong consequence roadmap. It does not import a second theorem spine into 42 and does not function as a proof source for Sections~1--9.
\end{fixedbox}

\subsection*{Scope and dependency declaration}
The fixed-domain object is an admissible evaluation regime in which projection descends through quotient structure, standing has grounded origin conditions, symmetric branching blocks singular self-location without added selector structure, and anchor/tensor/skin stratification is already available. This appendix depends on Sections~5, 8, and the ATS-derived role discipline carried in the main text.

\subsection*{Claim type}
This appendix is a theorem roadmap with consequence-facing summary. It records the exact downstream payoff of \minddoc{} without reproducing its full proof-granularity ladder.

\begin{proposition}[Mind roadmap consequence]
Relative to the capstone substrate, mind is to be read as a structurally rigid interface of admissible evaluation: projection descends through quotient structure, persistence requires non-derivative standing bearers, symmetric branching blocks selector-free singular self-location, identity does not duplicate without invariant asymmetry or standing failure, and anchor/tensor/skin stratification is forced rather than optional vocabulary.
\end{proposition}

\begin{proof}
This is the integrated payoff of \minddoc{}. The source develops quotient descent, standing-origin necessity, symmetric self-location impossibility, escape exhaustion, non-duplication of identity, anchor--tensor--skin stratification, and structural rigidity from one admissible evaluation regime. For 42, the important point is not to restage that proof ladder, but to register its consequence-facing reading: once the closure substrate is fixed, mind is not a free-floating extra ontology but a rigid interface condition on admissible evaluation. By Theorem~\ref{thm:no-downstream-backflow}, the roadmap status preserves that payoff without importing a second foundational proof spine.\cite{MaleyMindRigidInterface}
\end{proof}

\begin{reviewbox}
\textbf{Exact non-claims.} This appendix does not claim to derive consciousness from below, identify a neural substrate, or replace the capstone's own foundational arc. Its narrower role is to record the structural mind theorem as a downstream roadmap whose proofs remain in the source manuscript.\cite{MaleyMindRigidInterface}
\end{reviewbox}
