\section{Downstream reading path and appendix guide}
\label{app:reading-path}
\begin{fixedbox}
\textbf{Downstream consequence-facing only.} This appendix is archival packaging downstream of Sections~1--9 and Section~\ref{sec:consequence-pathways}. It records downstream consequence routing or audit posture only and does not function as a live proof source for the foundational arc.
\end{fixedbox}

\subsection*{Shortest authoritative reading path}

\begin{enumerate}
  \item Front matter: title page and abstract.
  \item \S\,1 for claim class, scope posture, source-role discipline, and the theorem arc.
  \item \S\,2 for the target class, kernel floor, non-derivability, and mechanization boundary.
  \item \S\,3 for modeling necessity, identity persistence, irreversible commitment, and the coherence theorem family.
  \item \S\,4 for the AMetric boundary, relabeling-indifference collapse, and the no-deeper-invariant theorem.
  \item \S\,5 for gate existence, standing emergence, standing--admissibility equivalence, quotient / factorization closure against same-scope discriminators, unique interior, and the compressed no-alternative-architecture theorem.
  \item \S\,6 for operator exhaustion and mathematics closure.
  \item \S\,8 for same-domain meta-closure and the non-instantiability theorem.
  \item \S\,9 for the two-spectrum synthesis and the descriptive-closure theorem.
  \item \S\,10 only if downstream main-body placement matters to the reader's objection.
  \item \S\,11 together with Appendices~\ref{app:dependency-register}, \ref{app:formalization-map}, \ref{app:attack-map}, \ref{app:reading-path}, and \ref{app:final-source-freeze} for the audit architecture, the axiom-necessity layer, and the formal closed-system seal.
  \item Appendix~\ref{app:downstream-atlas-overview} and the later atlas appendices only after the foundational arc is fixed.
\end{enumerate}

This path verifies the capstone as one forced closure theorem before any downstream roadmap or consequence profile is read in detail.

\subsection*{Application-specific reading after the foundational arc}

\begin{enumerate}
  \item If the objection targets the periodic Navier--Stokes consequence, read \S\,10 and then \nsdoc{} beginning with its page-1 claim-type block, same-object convention, compressed proof spine, theorem map, and denial map.
  \item If the objection targets the Yang--Mills consequence, read \S\,10 and then \ymmaindoc{} together with the proof-home role splits recorded in \ymcompanionone{}, \ymcompaniontwo{}, and \ymcompanionthree{}.
  \item If the objection targets the main-body measurement consequence, read \S\,10 and then \measurementdoc{} beginning with the fixed downstream substrate, the measurement-reference quotient theorem, the Everettian non-selection theorem, the fixation-commutation criterion, and the selector-exhaustion taxonomy.
  \item If the objection targets a Zenodo-only appendix-atlas consequence, begin with Appendix~\ref{app:downstream-atlas-overview}, then read the relevant appendix, and only then consult the cited source manuscript beginning from its own fixed-domain declaration and non-claims.
\end{enumerate}

\subsection*{Appendix guide}

\begin{longtable}{P{0.28\textwidth}P{0.62\textwidth}}
\caption{Downstream appendix guide for the 42 consequence-atlas version}\\
\toprule
\textbf{Appendix} & \textbf{What it does} \\
\midrule
\endfirsthead
\toprule
\textbf{Appendix} & \textbf{What it does} \\
\midrule
\endhead
\bottomrule
\endfoot
Downstream consequence register & States the one-directional theorem arc and the first downstream consumers of each main section. \\
Downstream formalization map & States exactly what Lean surfaces are documented and at what level. \\
Downstream hostile-reader attack map & Lists the named denial targets for foundational and downstream objections. \\
Downstream reading path & Gives the shortest authoritative route through the manuscript and the post-foundational application reading order. \\
Downstream source-role and proof-home note & Declares which documents remain live theorem sources, which remain consequence-facing only, and which are excluded from the present dependency chain. \\
Downstream appendix atlas & States the governing exhaustion schema and the no-backflow rule for every later consequence appendix. \\
Measurement appendix & Records the measurement-reference quotient, Everettian non-selection, fixation commutation, and theory-level confirmation payoff. \\
Entanglement appendix & Records the Bell-scope joint-standing-class reading and the elimination of hidden-variable, signaling, mechanism, and repair readings on the same scope. \\
Gauge / constraint appendix & Records the roadmap-level payoff for canonical GR and selector-bearing quantum structure relative to admissibility-derived rigidity. \\
Interior-bounds appendices & Record the beginning-side L-metric boundary and the end-side exhaustion of admissible redescription without origin or termination narratives. \\
Baryogenesis appendix & Reclassifies matter--antimatter asymmetry as a standing-preserving identity consequence under irreversible cosmic evolution. \\
Black-hole appendix & Reclassifies horizons as fixation boundaries and dissolves the information paradox without changing exterior black-hole physics. \\
Life appendix & Records standing localization, life as minimal standing instantiation, and the constrained roles of intelligence and technology. \\
Mind appendix & Preserves the roadmap-level structural mind theorem without importing a second foundational proof ladder. \\
Meta-necessity appendix & Records the proof-of-proof corollaries on irreversibility, temporal asymmetry, and informational non-primitivity. \\
Dark-sector appendix & Records the meta--mystery and dark-sector eliminative constraints as late consequence diagnostics. \\
References & Bibliography for the final manuscript. \\
\end{longtable}