\section{Introduction and scope}

This manuscript is meant to be read as one forced theorem chain. Its burden is not to advertise a family resemblance among companion papers, but to state in one place and in strict order how the following claims hang together: the target class of reasoning is forced rather than protectively narrowed; the kernel of admissibility, standing, reference, and irreversibility is non-derivable from below; coherent reasoning therefore acquires a canonical state-transition form; the pre-fixational side is AMetric; the same-scope standing regime has one gate, one standing quotient, and one admissible interior; mathematics and physics are both closed under the same non-generative invariant; same-domain code, semantic, infinitary, and extension escape is exhausted; and the post-closure relation between mathematics and physics is a two-spectrum classification of admissible description rather than a grounding hierarchy.

The manuscript is therefore not a survey and not a mere corpus index. For the core theorem spine carried in Sections~\ref{sec:kernel-floor}--\ref{sec:meta-closure}, the present manuscript is the proof home. Companion manuscripts remain relevant only where later sections explicitly keep downstream theorem families imported or consequence-facing. Where a theorem family is imported, the import is typed as downstream support only and is not permitted to backflow into the foundational arc.

For hostile reading, the source posture is simple. Sections~\ref{sec:kernel-floor}--\ref{sec:meta-closure} now carry the core theorem spine locally. Later imported material is downstream only: theorem roadmaps, consequence profiles, or synthesis layers whose removal would not alter the foundational chain. The full source-by-source routing, proof-home allocation, and import boundaries are recorded in the dependency register and final source freeze rather than expanded here in the introduction.


A second editorial rule governs every downstream mention in the capstone. Whenever a source manuscript is cited as a theorem roadmap or consequence profile, the capstone preserves the source-level theorem object, claim class, endpoint hygiene, denial map, and non-claims rather than rewriting them into generic capstone summary language. This matters most for Navier--Stokes and Yang--Mills, where the source manuscripts already state the exact theorem object and method-neutral claim class, and for measurement, where the source manuscript already fixes the target discourse, quotient theorem, and denial-condition matrix.


The theorem arc is strict:
\begin{enumerate}
  \item kernel necessity, derivational presupposition, non-derivability, and minimality;
  \item canonical state-transition form, identity persistence, irreversible commitment, and governance-level bivalence;
  \item pre-fixational non-reference, relabeling indifference, equality-pattern completeness, AMetric collapse, and no deeper invariant;
  \item gate existence, standing emergence, standing--admissibility equivalence, quotient / factorization closure against same-scope discriminators, no repairs / no generators / no carriers, and the unique admissible interior;
  \item partial-algebra envelope discipline, no internal totalization, conservative extension collapse, finite exhaustion schema, and mathematics closure;
  \item licensed metric description, physical non-generativity, and the descriptive role discipline needed for the physical spectrum;
  \item inferential-life exhaustion, closure-relevance transmission, code-role exhaustion, no admissible same-domain diagonalization, rescue-route exhaustion, and same-domain G\"odel non-instantiability;
  \item fixation split, two-spectrum exhaustion, closure parity, mirror classification, the prohibition package, post-closure practice, and descriptive closure;
  \item downstream consequence placement for Navier--Stokes, Yang--Mills, measurement, and Standard Model manuscripts; and
  \item formalization boundary, axiom-necessity layer, dependency register, hostile-reader denial map, shortest reading path, and source ledger.
\end{enumerate}

In particular, the capstone is not asking the reader to choose among rival interface designs. Section~\ref{sec:kernel-floor} fixes the target class and kernel floor as theorem-level boundaries of proposition-bearing reasoning, and Sections~\ref{sec:ametric-boundary}--\ref{sec:standing-regime} then show that, once one remains on the same fixed domain, no alternative admissibility architecture survives except by illicit import, same-side gate multiplication, repair / generator / carrier laundering, scope transport, or extensional collapse back to the unique gate. A hostile reader must therefore deny either the target phenomenon itself or a named theorem in the closure chain, not an allegedly open space of unexamined design options.

Two restrictions govern the whole paper.
\begin{enumerate}
  \item \textbf{No theorem-class drift.} Later sections are not allowed to sound like standard PDE, model-theoretic, or metaphysical papers unless their claim class really is PDE, model-theoretic, or metaphysical. The capstone is a closure theorem and keeps that identity all the way through.
  \item \textbf{No hidden proof-home inflation.} Companion proof homes may justify compact imported families, but they do not become silent premises merely because they exist. If a burden is not stated as imported, it is not live.
\end{enumerate}

The manuscript closes with two controlled downstream consequence placements. First, it states how the periodic Navier--Stokes and local sharp-local Yang--Mills manuscripts should be read: not as proof sources of the foundational arc, but as theorem roadmaps whose own claim-class discipline has already been hardened at source level. Second, it states how the measurement-reference and Standard Model manuscripts should be read: as compact consequence profiles clarifying what the closure theorem does to two very different application domains without changing the theorem class of the capstone itself.

What the paper is not. It is not a construction diary or a public build log. It is not a list of editorial scaffolding. It is not a claim that admissibility itself manufactures analytic estimates, physical dynamics, or metatheoretic encoding power. Every later section is constrained by that restriction.
