\section{Physics closure and descriptive role discipline}
\label{sec:physics-closure}

\subsection{Why physics appears only after mathematics closure}

Section~\ref{sec:operator-exhaustion} closed the same-scope operator question for mathematics. The present section asks the parallel physical question: once the unique admissible interior has already been fixed and no same-scope operator family can reopen it, what becomes of physical description itself? The answer must be narrower than an empirical theory of nature and stronger than a purely rhetorical claim that everything is bookkeeping. The burden here is classificatory and role-theoretic: to show, under the already fixed closure spine, what descriptive status physical structure may still carry without reopening standing. This section should therefore not be read as a second proof engine parallel to Sections~\ref{sec:kernel-floor}--\ref{sec:operator-exhaustion}. Its local task is to derive the descriptive-role discipline forced once the earlier theorem chain and the imported physical closure sources are already in place. The burden is to show that physical description may be rich, metric, analytic, and dynamically elaborate while still remaining non-generative with respect to standing.

This burden is classificatory rather than reconstructive.

This section classifies standing-bearing roles of physical descriptions under the fixed admissibility architecture; it does not introduce an independent generative theory of physical law.

What this section does not claim is equally important. It does not replace successful physical formalisms, derive new empirical predictions, or deny the mathematical and experimental richness of physical theory. Its burden is narrower: to classify which physical structures can still carry standing-bearing force once the earlier closure spine is fixed.

 Unlike the fully local forcing carried in Sections~\ref{sec:kernel-floor}--\ref{sec:operator-exhaustion} and Section~\ref{sec:meta-closure}, the present section does not introduce a second independent theorem engine beneath the physical applications. It states, under explicit theorem support, what physical description may and may not do once the prior closure spine is already fixed.

For this classificatory layer the live theorem support is limited and one-directional: \clausuradoc{} carries the metric-licensing and physics-closure hinge, \atsdoc{} contributes only the derived role discipline, and the Standard Model and measurement papers enter only as compact downstream applications rather than as independent proof engines.\cite{MaleyClausura,MaleyATS,MaleyStructura,MaleyMeasurement}

\subsection{Licensed metric description}

\begin{definition}[Licensed physical description]
A \emph{licensed physical description} is a same-scope physical presentation whose metric, analytic, probabilistic, state-descriptive, or representational content is admitted only inside an already fixed interior and only insofar as it preserves standing under lawful redescription. Such a description may be dynamically rich, but it does not thereby become a same-scope source of standing.
\end{definition}

\begin{definition}[L-metric articulation]
An \emph{L-metric articulation} is the admissible interior use of metric or analytic descriptors once the AMetric boundary has already been crossed and the relevant scope has been fixed. It is licensed exactly as interior bookkeeping and comparison structure, not as a boundary selector or primitive same-scope authorizer.
\end{definition}

\begin{theorem}[Licensed metric description theorem]
\label{thm:licensed-metric-description}
Within the fixed admissibility-governed interior, metric, probabilistic, analytic, and state-descriptive structure may appear only as licensed interior bookkeeping. In particular, no such structure is primitive at the boundary and none can function as a same-scope authorizer of standing.
\end{theorem}

\begin{proof}
At the boundary, the capstone has already fixed a binary, non-eventful, and non-transmissive AMetric interface: there is no admissibility-relevant selector, ranking, grading, metric, or operator there. So any metric or analytic object that is asked to determine standing before admissibility is fixed would reintroduce exactly the kind of parameterization or boundary action already blocked in Section~\ref{sec:ametric-boundary}.

Suppose, then, that metric or analytic structure is introduced only after admission. If it is now asked to decide which acts stand, then it functions as a carrier attempt in the sense of Section~\ref{sec:standing-regime}: it becomes a primitive authorizer distinct from the unique same-scope gate. But the no-carriers theorem already rules that out. So the only admissible remaining role for such structure is licensed interior bookkeeping: it can describe, compare, coordinate, track, or calculate within the admitted interior, but it does not thereby become an independent same-scope source of standing-bearing force.

This is precisely the physical-side content imported from \clausuradoc{} in capstone language: the L-metric boundary licenses metric articulation without making it generative. Hence metric, probabilistic, analytic, and state-descriptive structure are licensed only as interior bookkeeping and may not function as primitive same-scope authorizers of standing.
\end{proof}

\begin{corollary}[No cross-fixation comparability from metricity alone]
Metric articulation is fixation-local. If a fixed physical scope admits metric description, that does not by itself license cross-fixation comparison, cross-domain identification, or global ontic transport.
\end{corollary}

\begin{proof}
A cross-fixation comparison would require an additional same-scope identification aligning relata, comparison standards, or domain structure across more than one fixation. But metricity alone is only licensed interior description within a fixation. Without an independently licensed cross-scope gate, metricity therefore cannot by itself authorize cross-fixation comparison or transport. So the admissible role of metric articulation remains fixation-local.
\end{proof}

\subsection{Physical description is non-generative}

\begin{definition}[Physical non-generativity]
A fixed-scope physical description is \emph{non-generative} iff it does not create, amplify, repair, transfer, or primitively authorize standing. It may coordinate already admitted content, but it cannot produce new same-scope standing-bearing force.
\end{definition}

\begin{theorem}[Physical non-generativity theorem for admissible physical description]
\label{thm:physical-non-generativity}
No admissible physical description on the fixed scope becomes an independent same-scope source of standing-bearing force by metric articulation, typicality, boundary narrative, ontic carrier laundering, or descriptive enrichment alone. All admissible physical descriptions are therefore standing-preserving bookkeeping within the unique admissible interior unless they openly change scope by adding new witness load, new selector structure, or new admissibility-bearing data.
\end{theorem}

\begin{proof}
Any alleged same-scope elevation of physical description into a standing-bearing authorizer would have to proceed by one of the routes already excluded elsewhere in the capstone. If it works by a derivative score, typicality, probability, fit, or threshold, then it is carrier laundering and is blocked by the no-carriers theorem. If it works by a story of metric emergence, boundary productivity, or pre-admissible dynamic crossing, then it violates the AMetric and non-eventful boundary theorem. If it works by transporting standing from another scope, another observational frame, or another descriptive envelope, then it is illicit scope transport and is blocked by the fixed-scope discipline. If it works by local redescription or by representational choice alone, then it violates skin non-authority and redescription neutrality.

So a physical description may be rich, but any same-scope standing-bearing force it is claimed to add must either collapse to already admitted bookkeeping or enter by explicit scope change. The latter case is not same-scope generation but a new regime. Hence admissible physical description is non-generative on the fixed scope: the theorem classifies what physical theories may do as admissible descriptions, not what physical reality must be independently of that classificatory setting.
\end{proof}

\begin{theorem}[Conditional locality eliminator]
\label{thm:locality-eliminator}
Assume locality is retained as a structural admissibility constraint on the fixed physical scope. Then any purported locality-preserving theory extension falls into exactly one of the following classes:
\begin{enumerate}
  \item it is redundant, adding no genuine new constraint content beyond locality itself;
  \item it requires hidden global coordination to remain coherent and therefore ceases to be locality-preserving; or
  \item it parasitically offloads its enforcement onto already fixed structure and therefore contributes no independent same-scope standing-bearing content.
\end{enumerate}
In no case does such an extension generate new same-scope standing-bearing physical content.
\end{theorem}

\begin{proof}
If an extension adds no genuine new constraint content beyond locality, then it is redundant by definition. If it does add such content, then that content must be coordinated somewhere. If the coordination is genuinely new and same-scope, the extension requires a global structure or external synchronization not already contained in purely local articulation; that breaks the locality hypothesis. If the extension instead claims to get its force ``for free'' from the already fixed locality discipline, then nothing new is enforced and the added structure is parasitic on the existing regime. These cases are exhaustive once locality is treated as a structural admissibility constraint. Therefore locality alone eliminates most purported same-scope physical extensions before empirical adequacy is even reached.
\end{proof}

\begin{remark}
The locality eliminator is conditional and secondary. It sharpens physics closure when locality is explicitly retained, but the general physical non-generativity theorem does not depend on it. The capstone therefore records it as an optional strengthening, not as the whole of physics closure.
\end{remark}


\begin{theorem}[Exhaustion of same-domain physical closure escapes]
\label{thm:physical-closure-escape-exhaustion}
Let $\Phi$ be any purported same-scope physical enrichment on the fixed domain that claims standing-bearing authority beyond the closure results of Sections~\ref{sec:ametric-boundary}--\ref{sec:operator-exhaustion}. Then exactly one of the following holds:
\begin{enumerate}
  \item $\Phi$ preserves anchors, tensor content, and standing and therefore collapses to licensed interior bookkeeping;
  \item $\Phi$ functions as a carrier attempt or other derived same-scope authorizer and is blocked by the no-carriers theorem;
  \item $\Phi$ reintroduces a boundary selector, metric primitive, ranking, or probabilistic authorizer and is blocked by the AMetric boundary;
  \item $\Phi$ depends on a representative-sensitive or non-factorizing discriminator and is blocked by standing-quotient uniqueness, skin non-authority, and same-scope factorization discipline;
  \item $\Phi$ adds a witness, selector, ontic privileging device, or other same-domain authority not already licensed on the fixed scope, and so is not an enrichment of the same scope but an illicit authority import or explicit scope change.
\end{enumerate}
No sixth same-domain physical escape route remains. In particular, every same-scope physical closure escape is either bookkeeping, already ruled out by earlier theorems, or not a same-scope counterexample at all.
\end{theorem}

\begin{proof}
If $\Phi$ preserves anchors, tensor content, and standing, then by the licensed-metric-description theorem and the derived role discipline it contributes no new standing-bearing force and is licensed interior bookkeeping. If instead $\Phi$ tries to decide which acts stand by means of a derived score, weight, confidence, probability, or comparable criterion, then it is a carrier attempt and is ruled out by Theorem~\ref{thm:no-independent-carriers}. If it shifts the work to a boundary ranking, metric, selector, or other admissibility-relevant parameter, then it reopens precisely the kind of pre-admissible structure excluded by Section~\ref{sec:ametric-boundary}. If it preserves present eligibility while distinguishing representative-sensitive or non-factorizing structure as standing-bearing, then it is blocked by Theorem~\ref{thm:standing-quotient-uniqueness}, Corollary~\ref{cor:skin-non-authority}, and Theorem~\ref{thm:same-scope-factorization-discipline}. The only remaining way to produce additional same-scope authority is to add witness load, ontic privileging, or some further admissibility-bearing structure not already licensed on the fixed scope. That is not a same-scope physical enrichment but either illicit same-domain authority import or explicit scope change. These cases are exhaustive because any purported physical closure escape must either preserve the fixed standing architecture, attempt to refine or replace it, or leave the fixed scope altogether.
\end{proof}


\subsection{Derived role discipline for physical description}

\begin{definition}[Anchor / tensor / skin in physical description]
Within a fixed physical scope, anchors are the non-violable preconditions of admissible description, tensors are the quotient-level invariant content and compatibility relations that carry standing-relevant load, and skin is representational surplus whose alteration changes no same-scope standing-bearing consequence.
\end{definition}

\begin{theorem}[Derived role-discipline theorem for physical description]
\label{thm:ats-physical}
Every admissibility-preserving same-scope physical description factors through the anchor / tensor / skin decomposition, and no fourth admissibility-bearing role exists there. In particular:
\begin{enumerate}
  \item anchors are preconditions of admissibility rather than objects of same-scope explanation or optimization;
  \item tensors are quotient-level invariant content rather than mechanisms or operators; and
  \item skin is expressive surplus with zero same-scope standing-bearing authority.
\end{enumerate}
This role discipline is derived and non-generative: it introduces no new admissibility question and no new admissibility level.
\end{theorem}

\begin{proof}
The role-decomposition theorem from \atsdoc{} already shows, within fixed-scope admissibility-governed regimes, that every admissible description decomposes into anchors, tensor content, and skin, uniquely up to lawful redescription. Its minimality theorem shows that no fourth role remains, because any purported additional role must either change definedness (hence anchor), change same-scope admissible consequences (hence tensor), or change neither (hence skin).

Applying that result to physical description adds no new generative power. On the contrary, it forbids the two most common confusions at precisely the point where the descriptive role discipline matters. First, anchors are not new foundational objects to be explained from within the same scope; attempting to move them would require boundary action or illicit transport. Second, tensors are not operators or mechanisms; treating them as such would either introduce a new operator envelope or mis-type invariant content as generative. Third, skin cannot be promoted to standing-bearing authority without violating quotient factorization and same-scope uniqueness. So the role discipline is derived and non-generative: it classifies physical description after closure and does not create a fourth foundational level.
\end{proof}

\begin{corollary}[Tensors are not operators; mechanism language is skin unless typed otherwise]
A tensor may constrain admissible physical description by quotient-level invariance and compatibility, but it is not itself an operator envelope. Mechanism language may therefore appear only as explicitly non-load-bearing skin unless an actual licensed operator envelope has already been fixed independently.
\end{corollary}

\begin{proof}
If a tensor were treated as an operator, it would either act without licence, which is inadmissible, or else require a new licensed operator envelope. In the latter case the purported mechanism is either just an already fixed operator under another name or a new same-scope extension, which is blocked by exhaustion. So tensors are not operators. Correlatively, mechanism language may be used only as skin unless a genuine operator envelope has already been independently licensed.
\end{proof}

\subsection{Standard Model bookkeeping as a worked transport-closure example}

\begin{proposition}[Witness-normal-form collapse in the fixed Standard Model load]
\label{prop:sm-witness-collapse}
Within the fixed renormalizable chiral gauge load audited in \structuradoc{}, apparent same-scope Standard Model parameter freedoms collapse to a witness-normal form under admissible redescription and explicit transport. In particular, the low-energy and fixed-load witness results may be read in the following capstone form.
\begin{center}
\renewcommand{\arraystretch}{1.18}
\begin{tabularx}{0.96\textwidth}{P{0.29\textwidth}P{0.28\textwidth}Y}
\toprule
\textbf{Sector} & \textbf{Witness-normal form} & \textbf{Capstone reading} \\
\midrule
Charged current & $G_F$ & The pair $(g_2,v)$ overcounts same-scope load in the contact-interaction regime; the standing-bearing content collapses to the Fermi witness. \\
Electromagnetic sector & $e$ & The pair $(g_1,g_2)$ overcounts same-scope electromagnetic load once the pure-photon scope is fixed. \\
Yukawa / mass presentation & transport-equivalent mass and Yukawa witnesses & The two presentations are same-scope bookkeeping variants rather than independent standing-bearing structures. \\
QCD CP-odd sector & $\bar\theta$ & The physically relevant CP-odd QCD content collapses to one invariant witness. \\
Flavor and oscillation sector & oscillation invariants & Same-scope flavour descriptions collapse to the invariant oscillation family rather than to presentation-dependent coordinates. \\
Broken-gauge high-energy sector & longitudinal--Goldstone amplitude-class equivalence & The two presentations remain transport-equivalent amplitude bookkeeping within the fixed admitted scope. \\
\bottomrule
\end{tabularx}
\end{center}
Moreover, anomaly cancellation and Yukawa compatibility force the hypercharge class in the minimal chiral skeleton, hypercharge normalization is redundant, and tree-level FCNC are excluded at the fixed load.
\end{proposition}

\begin{proof}
This is the capstone reading of the transport-certificate ledger in \structuradoc{}. Each collapse is exhibited there by the same pattern: the input skin is named, an admissible transport map is written, the invariant witness set is computed, and witness rank is compared to apparent parameter rank. The charged-current and electromagnetic examples show directly that pairs such as $(g_2,v)$ and $(g_1,g_2)$ overcount standing-bearing content on restricted scopes because only one witness survives transport on the fixed scope. The Yukawa/mass, $\bar\theta$, oscillation, and longitudinal--Goldstone subsectors repeat the same pattern in more structured settings. The forced discrete skeleton then shows that anomaly cancellation and Yukawa compatibility fix the hypercharge class and leave no room for a further same-scope equivalence completion within the declared load. So the Standard Model application does not create new physics-closure burden; it exhibits the already proved non-generativity theorem in a worked transport ledger.
\end{proof}

\begin{corollary}[No further same-scope equivalence completion in the fixed Standard Model load]
Within the declared renormalizable Standard Model load, no further same-scope equivalence completion remains without adding new witness load, leaving the scope, or invoking a standing-failure mode.
\end{corollary}

\begin{proof}
Once witness-normal form has been reached, any further same-scope equivalence completion would have to preserve standing while collapsing distinctions not already removed by the transport certificates. But by the same ledger, any such further collapse either adds no new witness information and is redundant, or alters the witness set and is therefore a scope change, or else relies on privileged representation or hidden load and is a standing failure. So no further same-scope equivalence completion remains.
\end{proof}

\subsection{Measurement as a problem of reference}

\begin{definition}[Physically non-selective theory]
A theory is \emph{physically non-selective} with respect to a measurement episode if it realizes multiple stable post-measurement record-bearing histories while supplying no physical law, state variable, or dynamically privileged trajectory that singles out one such history as the unique referent of the pre-measurement diachronic discourse.
\end{definition}

\begin{theorem}[Measurement-reference application theorem]
\label{thm:measurement-reference-application}
If a physically non-selective theory is used to underwrite truth-apt diachronic discourse in which measurement records function as theory-level evidential anchors, then admissible reference assignments for those records must collapse into a single standing-bearing quotient class on the fixed scope. If they do not, then confirmation, memory, anticipation, and deliberation become assignment-relative rather than theory-relative.
\end{theorem}

\begin{proof}
The measurement source proves that admissible reference assignments form a fixed-domain space whose standing-bearing content factors through a unique measurement-reference quotient. It also proves that confirmational-role divergence is quotient-relevant rather than semantic skin: if admissible assignments induce different comparative evidential roles, then they belong to distinct standing-bearing quotient classes. In a physically non-selective theory, the bare dynamics may stabilize multiple branch-local records without supplying a selector that fixes which one is the diachronic referent of the pre-measurement discourse. Bare Everett is the paradigmatic example.

If the admissible assignments nevertheless remain multiple in a quotient-relevant way, then the same physical episode supports different standing-bearing evidential uses, so theory-level confirmation is no longer fixed by the theory as such. By the same fixed-domain theorem family, memory, anticipation, and agency inherit that same lineage dependence. Therefore either admissible assignments are restricted strongly enough that fixation commutes with lawful redescription and the quotient collapses to one standing-bearing class, or else the discourse becomes assignment-relative rather than theory-relative.
\end{proof}

\begin{corollary}[Bare physical multiplicity does not yet fix evidential reference]
Branch-local determinacy, decoherence-based record stability, centered descriptions, self-location, and decision-theoretic branch-weighting do not by themselves fix diachronic evidential reference. They presuppose successor typing and record reference rather than creating them.
\end{corollary}

\begin{proof}
The measurement source shows that branch-local determinacy and diachronic referential determinacy are distinct. Bare Everettian dynamics and decoherence yield stable local records, but they remain physically non-selective with respect to which record is the referent of pre-measurement evidential discourse. Centered descriptions, self-location, and branch-weighting presuppose a domain of already typed successors and records over which they distribute centers, credences, or utilities. So these devices are downstream of referential fixation rather than solutions to it.
\end{proof}

\subsection{Physics closure}

\begin{theorem}[Physics closure theorem]
\label{thm:physics-closure}
Physical description is closed under the same invariant that already closed mathematics: no same-scope physical description becomes a new standing-bearing authorizer. More precisely, within the unique admissible interior every purported same-scope physical enrichment is exactly one of the following:
\begin{enumerate}
  \item licensed interior bookkeeping or redescription that preserves anchors, tensor content, and standing;
  \item a carrier attempt, boundary selector, or metric/probabilistic authorizer blocked by the earlier sections;
  \item an added witness, selector, ontic privileging device, or admissibility-bearing structure that therefore changes scope rather than enriching the same scope.
\end{enumerate}
No fourth same-scope physical status remains.
\end{theorem}

\begin{proof}
The first case is exactly the licensed metric description theorem together with the derived role discipline: physical description may be rich, but if it preserves anchors, tensor content, and standing, it is licensed interior bookkeeping. The second case is excluded by the AMetric boundary theorem, the no-carriers theorem, the no-repair and no-generator theorems, and the measurement source's no-selector consequences for physically non-selective theories. The third case is not same-scope enrichment at all; it is explicit scope change because it adds new witness content or new admissibility-bearing structure.

These cases are exhaustive. A purported same-scope physical enrichment must either preserve standing while adding no new standing-bearing content, or else attempt to authorize standing by a new same-scope source, or else enlarge the witness-bearing content of the scope. Since the second class is blocked and the third is scope change, only licensed non-generative description remains. Therefore admissible physical description is closed under the same invariant already governing mathematics: no same-scope physical description becomes an independent same-scope source of standing-bearing force. This is a theorem about the classificatory role of physical description inside the admissible regime, not an ontological theorem asserting that physical reality is exhausted by bookkeeping.
\end{proof}



\begin{remark}[Claim posture of this section]
Theorems in this section are local only in the following sense: they classify what descriptive and metric structure may still do once the earlier closure layers are fixed. The section does not claim to reproduce, inside the present manuscript alone, every physics-facing source derivation that motivated those classifications. Its force is therefore controlled and one-directional: the core spine constrains the physical layer, while the physical layer is not allowed to back-support the spine.
\end{remark}

