\begin{abstract}
This manuscript now functions as the local proof home for the core theorem spine. Sections~1--8 carry the load-bearing chain in-manuscript: the non-derivable kernel of admissibility, standing, reference, and irreversibility; canonical state-transition form with identity persistence, irreversible commitment, and fail-closed bivalence; the AMetric boundary and equality-pattern collapse; standing as reuse-stable admissibility together with no repair, no generators, no carriers, quotient uniqueness, and the unique admissible interior; closure of mathematics by same-scope operator exhaustion; and explicit defeat of same-domain meta-escape, including the non-instantiability of G\"odel-style closure threats inside the unique admissible interior. Between the interface and operator layers, the manuscript also makes explicit the fixed-domain closure claim that no alternative same-domain admissibility architecture survives except by illicit structure import, collapse of the base goods, or extensional identity with the unique gate.

Downstream consequence layers are preserved but not allowed to function as hidden proof sources for that spine. Physics closure, two-spectrum synthesis, and the Zenodo appendix atlas are therefore consequence-facing and classificatory under the fixed theorem chain of the main text rather than additional foundational engines. The downstream layer places four consequence manuscripts without theorem backflow: Navier--Stokes and Yang--Mills appear as theorem roadmaps whose claim-class discipline, endpoint hygiene, denial maps, and non-claims are preserved rather than re-authored here; measurement and Standard Model manuscripts appear as compact consequence profiles whose fixed-domain hardening is carried over only at theorem level. A Zenodo-only appendix atlas then extends the consequence layer across measurement-record fixation, Bell-scope entanglement, gauge/constraint rigidity payoffs, admissible interior bounds, baryogenesis, black-hole fixation, standing localization, mind, meta-necessity, and dark-sector elimination. None of those downstream appendix manuscripts functions as a proof source for Sections~1--9, and each may be removed without altering the foundational arc. The appendices therefore expose a controlled consequence atlas together with the dependency register, formalization boundary, attack map, shortest reading path, and final source ledger.
\end{abstract}
